---
title: "Final Report for Intro to Data Science"
output:
  html_document:
    df_print: paged
---


```{r}
library(tidyverse)
myurl <- "https://raw.githubusercontent.com/reisanar/datasets/master/WorldCupMatches.csv"
worldcup <- read.csv(myurl)
```


```{r}
worldcup
```
Look at the `world_bank_pop` function

```{r}
world_bank_pop
```
Look at the `WorldPhone` function
```{r}
WorldPhones
```
















Take a glimpse of worldcup

```{r}
glimpse(worldcup)
```
Arrange world cup in `Year, Datetime, Stage, Stadium`

```{r}
arrange(worldcup, Year, Datetime, Stage, Stadium)
```
arrange `Home.Team.Goals and year` in descending order

```{r}
arrange(worldcup, desc(Home.Team.Goals, Year))
```
Select everything that ends with `Goals`

```{r}
select(worldcup,
      Home.Team.Goals:Away.Team.Goals,
      ends_with("Goals"),
      Half.time.Home.Goals,
      Half.time.Away.Goals)
```

create a function called `worldcup_data`

```{r}
worldcup_data = select(worldcup,
                       Home.Team.Goals:Away.Team.Goals,
                       ends_with("Goals"),
                       Half.time.Home.Goals,
                       Half.time.Away.Goals)
worldcup_data
```

mutate a function called `Total_fh_goals` and `Total_ht_goals` which make the first value add `Home.Team.Goals` and `Away.Team.Goals` second value add `Half.Time.Home.Goals` and `Half.time.Away.Goals`

```{r}
mutate(worldcup_data,
       Total_fh_goals = Home.Team.Goals + Away.Team.Goals,
       Total_ht_goals = Half.time.Home.Goals + Half.time.Away.Goals
       )
```
Find the mean of Home.Team.Goals

```{r}
summarise(worldcup, hometeamgoals = mean(Home.Team.Goals, na.rm = TRUE))
```
group Year and find the avg

```{r}
worldcup %>%
  group_by(Year) %>%
  summarize(
    count = n(),
    avg = mean(Year, na.rm = TRUE)
  )
```

List only the first 10 of the Dataset

```{r}
head(worldcup, 10)
```


Filter all the `Argentina` games


```{r}
filter(worldcup, Home.Team.Name == "Argentina")
```

Filter all the `Away.Team.Name` of Argentina

```{r}
argen1 = worldcup %>%
  filter(Away.Team.Name == "Argentina")
argen1
```
Create a geom_point() to see the Goals scored each year for the Away.Team.Goals for Argentina

```{r}
ggplot(data = argen1) +
  geom_point(aes(x = Year, y = Away.Team.Goals))
```


Create function named `argen` that Lists only `Argentina`


```{r}
argen = worldcup %>%
  filter(Home.Team.Name == "Argentina")
argen
```
Filter all attendance greater than 67800

```{r}
worldcup %>%
  filter(Attendance > 67800)
```
Arrange to show the most Home.Team.Goals

```{r}
arrange(worldcup, desc(Home.Team.Goals))
```

make a geom_point() with x being `Year` and y being `Home.Team.Goals`

```{r}
ggplot(data = argen) +
  geom_point(aes(x = Year, y = Home.Team.Goals))
```

filter all `Home.Team.Name` for `Portugal`

```{r}
portg = worldcup %>%
  filter(Home.Team.Name == "Portugal")
portg
```
Filter all `Away.Team.Name` for `Portugal`

```{r}
portg1 = worldcup %>%
  filter(Away.Team.Name == "Portugal")
portg1
```

make a geom_point() with the portg1 function with x being `Year` and y being `Away.Team.Goals`

```{r}
ggplot(data = portg1) +
  geom_point(aes(x = Year, y = Away.Team.Goals))
```
Filter just the `Old Trafford Stadium`

```{r}
stad = worldcup %>%
  filter(Stadium == "Old Trafford Stadium")
stad
```
Create a boxplot with x being `Stadium` and y being `Attendance`

```{r}
ggplot(data = stad) +
  geom_boxplot(aes(x = Stadium, y = Attendance))
```




```{r}
all_arg_players = worldcup %>%
  filter(Home.Team.Name == "Argentina")
all_arg_players
```

```{r}
all_por_players = worldcup %>%
  filter(Home.Team.Name == "Portugal")
all_por_players
```


```{r}
worldcup %>%
  filter(Year == 1990, Home.Team.Name == "Argentina")
```
create a geom_point() x being `Year` and y being `Home.Team.Goals`

```{r}
ggplot(data = portg) +
  geom_point(aes(x = Year, y = Home.Team.Goals))
```
Filter `RoundID > 300` and `Away.Team.Initials == "ARG"`

```{r}
worldcup %>%
  filter(RoundID > "300", Away.Team.Initials == "ARG")
```


```{r}
worldcup %>%
  filter(RoundID > "300", Away.Team.Initials == "POR")
```

create a geom_point() and make x `Year` and `Attendance`

```{r}
ggplot(data = worldcup) +
  geom_point(aes(x = Year, y = Attendance))
```
Filter `Year > 1996` and `RoundID > 6000`

```{r}
worldcup %>%
  filter(Year > 1996, RoundID > 6000)
```

Create geom_point() `City` as color `size` as `Home.Team.Goals` and `alpha = 0.9`


```{r}
ggplot(data = worldcup) +
  geom_point(aes(x = Year, y = Attendance,
                 color = City, size = Home.Team.Goals),
             alpha = 0.9)
```
Which team had the most Home Team Goals?

```{r}
worldcup %>%
  arrange(desc(Home.Team.Goals))
```
Which team had the most Away Team Goals?


```{r}
worldcup %>%
  arrange(desc(Away.Team.Goals))
```

Make a bar graph for Year

```{r}
ggplot(data = worldcup) +
  geom_bar(aes(x = Year))
```
Count the total amount of Referees

```{r}
worldcup %>%
  count(Referee)
```
Create a histogram for the Attendance

```{r}
ggplot(data = worldcup) +
  geom_histogram(aes(x = Attendance))
```
Use a dark green color to draw a geom_point

```{r}
ggplot(worldcup, aes(x = Year, y = Attendance)) + 
  geom_point(color = "darkgreen")
```



Change the title to home team goals and use a bargraph

```{r}
ggplot(worldcup, aes(x = Home.Team.Goals)) + 
  geom_histogram(fill = "green", color = "blue") + 
  ggtitle("Home Team goals") + 
  xlab("Goals") + xlim(c(0, 10))
```

Create a scatter plot for Away Team Goals


```{r}
ggplot(worldcup, aes(x = Home.Team.Goals, y = Half.time.Home.Goals)) + 
  geom_point()
```
select all rows except Referee

```{r}
worldcup %>%
  select(-Referee)
```


